---
title: "githubpage_test file"
author: "Paul Schuette"
date: "May 18, 2018"
output: html_document
---

Ctrl-Alt-I is a keyboard shortcut for creating a chunk of r code

```{r message=FALSE}
  library(leaflet)
  library(dplyr)
  library(tidyr)
  library(ggplot2)
  library(DT)
```

Then, let’s create the data.frame we’re going to use to plot:

```{r}
esc <- read.csv("data/escapement_counts.csv", stringsAsFactors = FALSE)
```

If you haven’t saved the data locally, you can load it directly from the KNB using this line:

esc <- read.csv(url("https://knb.ecoinformatics.org/knb/d1/mn/v2/object/knb.92020.1", method = "libcurl"), 
                stringsAsFactors = FALSE)

```{r}
esc %>% head()
```

  
Now that we have the data loaded, let’s calculate median annual escapement by species:
  
```{r}
median_esc <- esc %>% 
  separate(sampleDate, c("Year", "Month", "Day"), sep = "-") %>% 
  group_by(Species, SASAP.Region, Year, Location) %>% 
  summarize(escapement = sum(DailyCount)) %>% 
  group_by(Species) %>% 
  summarize(median_escapement = median(escapement))
```

```{r}
ggplot(median_esc, aes(Species, median_escapement)) +
  geom_col() +
  coord_flip()
```

Calculate median annual escapement by species using the dplyr package Let’s convert the escapement data into a table of just the unique locations:

```{r}
locations <- esc %>% 
  distinct(Location, Latitude, Longitude) %>% 
  drop_na()
```

```{r}
datatable(locations)
```

Then making a leaflet map is (generally) only a couple of lines of code:

```{r}
leaflet(locations) %>% 
  addTiles() %>% 
  addMarkers(~ Longitude, ~ Latitude, popup = ~ Location)
```


